Validation of marker gene expression

### 2025-09-15 analyses/cell-type-consensus/template-notebooks/marker-gene-validation.Rmd
change default back to SCPCP000001

---
title: "Validation of marker gene expression"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: hide
params:
  project_id: "SCPCP000006"
---

>>>>

---
title: "Validation of marker gene expression"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: hide
params:
  project_id: "SCPCP000001"
---
